Title

### 2020-12-14 documents/DraftReport.Rmd
Comment
Small stylistic edits to equations (thanks Hannah!)

- simulation write-up (amelia)
- results (abby/hannah)

@@

$$\text{Fledged}_t \sim \text{Poisson}(\lambda_{\text{fledglings}}) $$
The fecundity rate, *f*, is derived from the rate at which chicks fledge,
$$f=\frac{1}{2}\times\lambda_{\text{fledglings}}*\phi_{n}^{30}$$
where $\phi_{n}$ is the nest survival probability and we assume that the maximum nest age, the number of days the nest was active, is 30. 
The observation process for the daily nest surveys is modeled using a Bernoulli distribution, based on daily nest survival probabilities and the state of the nest during the previous survey occasion:

$$\text{NestStatus}_{n,d}\sim\text{Bernoulli}(\phi_{n}*\text{NestStatus}_{n,d-1})$$
where $\text{NestStatus}_{n,d}$ is the status of nest $n$ at survey occasion $d$, $\phi_{n}$ is the nest surivial probability, and $\text{NestStatus}_{n,d-1}$ is the state of nest $n$ at the previous survey occasion $d-1$.

@@

*Integrated population model*  
To estimate abundance of the overall population $N_{tot}$ at each time *t*, the parameter estimates from the productivity and mark-resight models are combined with the stage-specific abundane estimated using the N-mixture model in a stochastic leslie population matrix model.

@@

[IPM joint likelihood equation]
The overall likelihood for this hierarchical state-space model can be described as the product of the state and observation process models:
$$L_{IPM}(\text{y}, ~CH, ~\text{NestStatus}, ~\text{Fledged}|~N_{1},~N_{ad}, phi_1, phi_{ad}, f, p_{mr}, p_s, ~\lambda_{\text{fledglings}}, ~\phi_n) 
$$=$L_{Abundance}(\text{y}| ~N_1, ~N_{ad}, ~{p_s}, \phi_1,~\phi_{ad}, f)\times$$
$$L_{Productivity}(\text{NestStatus}, \text{Fledged} | ~\phi_{n}, ~\lambda_{\text{fledglings}}) \times$$
$$L_{Survival}(\text{y}|\text{z}, ~\phi_{ad}, ~p_{mr})$$

>>>>

- simulation write-up (amelia)
- results (abby/hannah) - Hannah: wrote out a rough draft of results, will revisit tomorrow, but got something down to start with

@@

$$\text{Fledged}_t \sim \text{Poisson}(\lambda_{\text{fledglings}}) $$
The fecundity rate, *f*, is derived from the rate at which chicks fledge,
$$f=\frac{1}{2}\times\lambda_{\text{fledglings}}\times\phi_{n}^{30}$$
where $\phi_{n}$ is the nest survival probability and we assume that the maximum nest age, the number of days the nest was active, is 30. 
The observation process for the daily nest surveys is modeled using a Bernoulli distribution, based on daily nest survival probabilities and the state of the nest during the previous survey occasion:

$$\text{NestStatus}_{n,d}\sim\text{Bernoulli}(\phi_{n}\times\text{NestStatus}_{n,d-1})$$
where $\text{NestStatus}_{n,d}$ is the status of nest $n$ at survey occasion $d$, $\phi_{n}$ is the nest surivial probability, and $\text{NestStatus}_{n,d-1}$ is the state of nest $n$ at the previous survey occasion $d-1$.

@@

*Integrated population model*  
To estimate abundance of the overall population $N_{tot}$ at each time *t*, the parameter estimates from the productivity and mark-resight models are combined with the stage-specific abundance estimated using the N-mixture model in a stochastic leslie population matrix model.

@@

[IPM joint likelihood equation]
The overall likelihood for this hierarchical state-space model can be described as the product of the state and observation process models:
$$L_{IPM}(\text{y}, ~CH, ~\text{NestStatus}, ~\text{Fledged}|~N_{1},~N_{ad}, ~\phi_1, ~\phi_{ad}, ~f, ~p_{mr}, ~p_s, ~\lambda_{\text{fledglings}}, ~\phi_n) \ = $$
$$L_{Abundance}(\text{y}| ~N_1, ~N_{ad}, ~{p_s}, ~\phi_1,~\phi_{ad}, ~f)\ \times$$
$$L_{Productivity}(\text{NestStatus}, ~\text{Fledged} | ~\phi_{n}, ~\lambda_{\text{fledglings}})\ \times$$
$$L_{Survival}(\text{y}|~\text{z}, ~\phi_{ad}, ~p_{mr})$$
